Model Search in Relational Domains

### 2016-10-22 deductions.tex
improved explanation in 5.1

The second advantage of Eq.~(\ref{eq:at2}) is that we can compute the
\emph{closure} operation for relational domains in a lazy manner. To
this end, we construct a $\subdomain=\makesubdomain_\domain(\subvars)$
which is sufficient to perform one step of the closure operation each
time the abstract transformer is applied.
%
For example, let us consider $\domain=\octagons[\{x,y,z\}]$ and
$\subvars=\{y\}$. An octagonal inequality relates at 
most two variables. Thus it is sufficient to consider the subdomain
$\makesubdomain_\domain(\{y\})=\octagons[\{y\}]\cup\octagons[\{x,y\}]\cup\octagons[\{y,z\}]$,
which will compute the one-step transitive relations of~$y$ with each
of the other variables. 
%
\Omit{
%TODO
Hence, we do not compute the full closure in the full 
domain $\octagons[\{x,y,z\}]$, but we compute only a single step of the closure when the abstract deduction transformer is applied.
%
Only if $\abstrans^\subdomain$ deduces new information about $x$ or $z$
then the next step of the closure will be 
}
If this indeed affects $x$ and~$z$ then their
relations will be inferred in a later step of the propagation
algorithm, thus gradually computing the closure.

>>>>

The second advantage of Eq.~(\ref{eq:at2}) is that we can compute the
\emph{closure} operation for relational domains in a lazy manner. To
this end, we construct a $\subdomain=\makesubdomain_\domain(\subvars)$
which is sufficient to perform one step of the closure operation each
time the abstract transformer is applied.
%
For example, let us consider $\domain=\octagons[\{x,y,z\}]$ and
$\subvars=\{y\}$. An octagonal inequality relates at 
most two variables. Thus it is sufficient to consider the subdomain
$\makesubdomain_\domain(\{y\})=\octagons[\{y\}]\cup\octagons[\{x,y\}]\cup\octagons[\{y,z\}]$,
which will compute the one-step transitive relations of~$y$ with each
of the other variables. 
%
Hence, when the abstract deduction transformer is applied we do not
compute the full closure in the full domain,
but we compute only a single step of the closure in a restricted
domain, which makes single deduction steps more efficient.
%
If $\abstransel{\subdomain}$ deduces new information about $x$ or $z$
then the next step of the closure will be computed by the worklist
mechanism of Algorithm~\ref{Alg:ms} that we describe next.

%If this indeed affects $x$ and~$z$ then their
%relations will be inferred in a later step of the propagation
%algorithm, thus gradually computing the closure.
